---
title: "HW5"
author: "2019150445/Shin Baek Rok"
date: '2020 12 4 '
output: pdf_document
---
```{r}
library(tidyverse)
library(stringr)
```
# 2.

### a)

##### 1)
Only one backslash: Escape the next character in R strings.
Two backslash: Escape the next character in R regex.
Three backslash: First two backslash means just backslash in regex, and third backslash escapes the next character.

##### 2)
 \"\'\\\\  will work since first backslash works as escape symbol to escape ', similarly second backslash works as escape symbol to escape ", and last four backslashes indicate just one backslash.
 
##### 3)
In regex, dot means any character. To match the character '.', we have to use \. . Thus \..\..\.. means dot,any character,dot,any character,dot,any character. For example, .x.y.z 


### b)

##### 1
```{r}
#1.
'^[aeiouAEIOU]'
#2.
'[^aeiouAEIOU]'
#3.
'[^e]ed$'
#4.
'(ing|ise)$'
```
##### 2)
```{r}
str_subset(words, "(cei|[^c]ie)")
str_subset(words, "[^c]ei")#exception
```

##### 3)
```{r}
str_subset(words,'qu')
str_subset(words,'q[^u]') #None
```

##### 4)
For example, word summarise is the British English definition of summarize. We can match this figure by 'ise$'

##### 5)
'^010\\-?\\d{4}\\-?\\d{4}$' will work well.
```{r}
s<-c('010-7173-2932','010-234-gsd9','010-3232-233','010-23232-2333','01017382928')
str_subset(s,'^010\\-?\\d{4}\\-?\\d{4}$')
```


### c)

##### 1)

? means 0 or 1, that is {0,1}
+ means 1 or more, that is {1,}
* means 0 or more, that is {0,}

##### 2)
```{r}
# 1. ^.*$ will match any string since . means any character and * means 0 or more.

# 2. '\\{.+\\}' will match at least one character that is enclosed in parentheses

# 3. \d{4}-\d{2}-\d{2} will match 0000-00-00 where 0 can be replaced in 0 to 9

# 4. "\\\\{4}" will match \\\\\\\\ since \\ means \ and {4} means repeat 4 times.
```


### d)

##### 1)

1.
```{r}
pattern<-"^x|x$"
str_subset(words,pattern)
#or
words[str_detect(words,pattern)]
```

2.
```{r}
pattern<-"^[aeiouAEIOU]|[^aeiouAEIOU]$"
str_subset(words,pattern) %>% head()
```

3.
```{r}
pattern<-"([aeiouAEIOU])"
str_subset(words,pattern) %>% str_replace_all("[aeiouAEIOU]","") %>% str_subset('[aeiouAEIOU]') #None

```


# 3.
```{r}
library(gutenbergr)
```

### 1)
```{r}
x<-gutenberg_metadata
x$gutenberg_id[x$title %>% str_detect('Pride and Prejudice') ] %>% na.omit() %>% .[1:6]
```

### 2)
```{r}
gutenberg_works(languages='en')$gutenberg_id[gutenberg_works(languages='en')$title %>% str_detect('^Pride and Prejudice$')]
```

### 3)
```{r}
book<-gutenberg_download(1342)
```

### 4)
```{r}
library(tidytext)
words<-book %>% unnest_tokens(word,text)
words %>% head()
```

### 5)
```{r}
words<-words %>% mutate(location=1:nrow(words))
words %>% head()
```

### 6)
```{r}
words<-words %>% anti_join(stop_words,by='word')
words %>% head()
```

### 7)
```{r}
words<-words %>% inner_join(get_sentiments('afinn'),by='word')
words %>% head()
```

### 8)
```{r}
words %>% ggplot(aes(location,value))+geom_point(size=.5)+geom_smooth()
```