---
title: "STAT346_hw2_2019150445"
author: "2019150445/ShinBaekRok"
date: '2020 10 2 '
output: pdf_document
---

# 1.
```{r}
library(gapminder)
data(gapminder)
library(dplyr)
```



  a)
```{r}
gapminder %>% group_by(continent) %>% summarize(n_distinct(country))
```



  b)
```{r}
gapminder %>% filter(continent=='Europe',year==1997) %>%
  arrange(gdpPercap) %>% head(n=1) %>% select(country) 
gapminder %>% filter(continent=='Europe',year==2007) %>% 
  arrange(gdpPercap) %>% head(n=1) %>% select(country)
```



  c)
```{r}
gapminder %>% filter(year%in% 1980:1989) %>% 
  group_by(continent) %>% summarize(mean(lifeExp))
```



  d)
```{r}
gapminder %>% mutate(GDP=gdpPercap*pop) %>% 
  group_by(country) %>% summarize(totalGDP=sum(GDP))%>%
  arrange(-totalGDP) %>% head(n=5)
```



  e)
```{r}
gapminder %>% filter(lifeExp>=80) %>% select(country,lifeExp,year)
```



  f)
```{r}
gapminder %>% group_by(country) %>% summarize(corr=cor(lifeExp,gdpPercap))%>%
  arrange(-abs(corr)) %>% head(10)
```



  g)
```{r}
gapminder %>% filter(continent!='Asia') %>% group_by(continent, year) %>%
  summarize(avg=mean(pop)) %>% arrange(-avg) 
```



  h)
```{r}
gapminder %>% group_by(country) %>% 
  summarize(sd=sd(pop)) %>% arrange(sd) %>% head(3)
```








# 2.
```{r}
library(nycflights13)
library(ggplot2) #To use ggplot package
data(flights)
data(planes)
data(weather)
```



  a)
```{r}
#dep_time=NA means that plane does not depart(Plane has cancelled).
x<-flights %>% group_by(month) %>%
  summarize(total=n(),frequency=sum(is.na(dep_time)),proportion=frequency/total)
x %>% head()
x %>% ggplot(aes(x=month,y=proportion))+geom_point()+geom_line()
```
Month 2(i.e.Febuary) is the highest. Month 10(i.e. October) is the lowest.
As we can see, Summer & Winter has high proportion of cancelled flights. We can interpret this as an impact of snow and storm.



  b)
```{r}
flights %>% filter(year==2013, !is.na(tailnum)) %>%
group_by(tailnum) %>%summarize(freq=n()) %>%
arrange(-freq)%>%head(1)
```

```{r}
library(lubridate) #To calculate each week.
flights$week<-make_date(flights$year,flights$month,flights$day) %>% week()#Add week column to flights .

#Next, filter tailnum='N725MQ' that traveled the most times from NYC in 2013 
#and plot the number of trips per week over the year 2013.
flights %>% filter(year==2013 & tailnum=='N725MQ') %>% group_by(week) %>%
  summarize(total_flight=n()) %>%
  ggplot(aes(x=week,y=total_flight))+geom_point()+geom_line()

```



  c)
```{r}
planes %>% select(tailnum, old=year) %>%
  inner_join(flights,by='tailnum') %>% arrange(old) %>% head(1)

sum(unique(flights$tailnum) %in% unique(planes$tailnum))
```



  d)
```{r}
#planes$year indicates the year that plane has manufactured.
planes$year %>% is.na() %>% sum()



table(planes$manufacturer) %>% data.frame() %>% arrange(-Freq) %>% head(5)



planes<-planes %>% count(manufacturer,year) %>% 
  mutate(manufacturer=ifelse(n<7,'Other',manufacturer))
# When n<7, manufacturer is classfied as Other.


planes %>% ggplot(aes(x=year,y=n,col=manufacturer)) + geom_line()

```

Since 1980's, Boeing is higher in almost all years than any other company.




  e)
```{r}

weather %>% filter(year==2013 & month==7) %>% ggplot(aes(temp))+geom_histogram(col='black')
#Temp distribution is Slightly skewed to the right.

weather %>% ggplot(aes(y=wind_speed)) + geom_boxplot()
# There are some outliers, let's see when wind_speed>1000.

weather %>% filter(wind_speed>1000)




weather %>% ggplot(aes(dewp, humid)) +geom_point()+geom_smooth(fill=NA)
#There seem to be a positive relationship between dewp & humid.

weather %>% ggplot(aes(precip,visib)) +geom_point()+geom_smooth(fill=NA)
#There seem to be there isn't any relationship between precip & visib
```




  f)
```{r}
weather1<-weather %>% filter(year==2013 & precip>0)
lubridate::make_date(weather1$year, weather1$month, weather1$day) %>% n_distinct()

weather %>% group_by(month) %>% summarize(visib_avg=mean(visib)) %>%
  ggplot(aes(month, visib_avg))+geom_line()+geom_point() 
```
Month 12, Month 1,2 are lowest. That means in winter season, visibility is low.



```{r}
weather<-weather %>% mutate(date=make_date(weather$year,weather$month,weather$day))

weather$wday<-weather$date %>% wday()
weather %>% group_by(wday) %>% 
  summarize(visib_avg=mean(visib)) %>% ggplot(aes(wday,visib_avg))+geom_line()+geom_point()
```

It seems like there is some difference between the day of week, but its lowest average is 9.15 & its highest average is 9.49.(Not that differ)







# 3.
```{r}
library(ggplot2)
data(diamonds)
```


  a)
```{r}
hist(diamonds$carat,col='steelblue')
```


  b)
```{r}
qplot(diamonds$depth)
```



  c)
```{r}
qplot(data=diamonds, x=cut, y=price, geom='violin', fill=cut)
```




# 4.
```{r}
library(MASS)
Cars93<-as_tibble(Cars93)
```



  a)
```{r}
Cars93 %>% ggplot(aes(MPG.highway,Price,size=Horsepower))+geom_point()
```



  b)
```{r}
Cars93 %>% ggplot(aes(MPG.highway,Price,size=Horsepower,col=Origin))+
  geom_point()
```



  c)
```{r}
Cars93 %>% ggplot(aes(MPG.highway,Price,size=Horsepower))+
  geom_point()+stat_smooth()
```




  d)
```{r}
Cars93 %>% ggplot(aes(MPG.highway,Price,col=Origin))+
  geom_point()+facet_grid(.~Origin)
```





  e)
```{r}
Cars93 %>% ggplot(aes(MPG.highway,Price, col=Origin))+
  geom_point()+geom_smooth(method='lm',fill=NA)+facet_grid(.~Origin)

```