---
title: "HW6"
author: "2019150445/Shin Baek Rok"
date: '2020 12 17 '
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ISLR)
library(caret)
library(boot)
```

# 1.
a)

```{r}
head(Default)
fit<-glm(default~income+balance,data=Default,family='binomial')
fit
```

b)
```{r}
#i)
test_index<-createDataPartition(Default$default,list=F)
Default_test<-Default[test_index,]
Default_train<-Default[-test_index,]

#ii)
fit_train<-glm(default~income+balance,data=Default_train,family='binomial')
fit_train

#iii)
probs <- predict(fit_train, Default_test, type = "response")
y_hat<-ifelse(probs>0.5,'Yes','No')
mean(y_hat!=Default_test$default)
```

c)
```{r}
replicate(3,{
  test_index<-createDataPartition(Default$default,list=F)
  Default_test<-Default[test_index,]
  Default_train<-Default[-test_index,]

  fit_train<-glm(default~income+balance,data=Default_train,family='binomial')
  probs <- predict(fit_train, Default_test, type = "response")
  y_hat<-ifelse(probs>0.5,'Yes','No')
  mean(y_hat!=Default_test$default)
})
```

Since we split test and train set by random, the test error rate can be variable. But it is quite simmilar.

d)
```{r}
test_index<-createDataPartition(Default$default,list=F)
Default_test<-Default[test_index,]
Default_train<-Default[-test_index,]

fit_all<-glm(default~.,data=Default_train,family='binomial')
probs<-predict(fit_all,Default_test,type='response')
y_hat<-ifelse(probs>0.5,'Yes','No')
mean(y_hat!=Default_test$default)
```
It depends on how you split the model, but it doesn't seem to change the test error that much. In other words, the student variable do not leads to a reduction in the test error rate.



# 2.
a)
```{r}
set.seed(1)
glm(default~income+balance,data=Default,family='binomial') %>% summary()
```
se for income coef=4.985e-06.
se for balance coef=2.274e-04.

b)
```{r}
boot.fn<-function(data=Default,index){
  glm(default~income+balance,data=Default, subset=index, family='binomial')$coef[-1]
}
```

c)
```{r}
boot(Default, boot.fn, 100)
```

d)
Obtained standard errors by two methods are quite similar.


# 3.
```{r}
library(tidyverse)
library(purrr)
library(pdftools)
library(dslabs)
library(lubridate)

fn <- system.file("extdata", "RD-Mortality-Report_2015-18-180531.pdf",
                  package="dslabs")
dat <- map_df(str_split(pdf_text(fn), "\n"), function(s){
  s <- str_trim(s)
  header_index <- str_which(s, "2015")[1]
  tmp <- str_split(s[header_index], "\\s+", simplify = TRUE)
  month <- tmp[1]
  header <- tmp[-1]
  tail_index  <- str_which(s, "Total")
  n <- str_count(s, "\\d+")
  out <- c(1:header_index, which(n == 1), 
           which(n >= 28), tail_index:length(s))
  s[-out] %>%  str_remove_all("[^\\d\\s]") %>% str_trim() %>%
    str_split_fixed("\\s+", n = 6) %>% .[,1:5] %>% as_tibble() %>% 
    setNames(c("day", header)) %>%
    mutate(month = month, day = as.numeric(day)) %>%
    gather(year, deaths, -c(day, month)) %>%
    mutate(deaths = as.numeric(deaths))
}) %>%
  mutate(month = recode(month, 
                        "JAN" = 1, "FEB" = 2, "MAR" = 3, 
                        "APR" = 4, "MAY" = 5, "JUN" = 6, 
                        "JUL" = 7, "AGO" = 8, "SEP" = 9, 
                        "OCT" = 10, "NOV" = 11, "DEC" = 12)) %>%
  mutate(date = make_date(year, month, day)) %>%
  filter(date <= "2018-05-01")
```

```{r}
#1.
glimpse(dat)
total<-as.numeric(dat$date) %>% range() %>% diff()
span<-61/total
fit<-loess(deaths~as.numeric(date),data=dat,span=span,degree=1)
dat<-dat[!is.na(dat$deaths),]
dat %>% mutate(smooth=fit$fitted) %>%
  ggplot(aes(as.numeric(date),deaths))+
  geom_point(alpha=.5)+
  geom_line(aes(as.numeric(date),smooth),col='red',size=1)


#2.
dat %>% mutate(smooth=predict(fit,as.numeric(dat$date))) %>%
  ggplot(aes(yday(date),deaths))+geom_point(alpha=.5)+
  geom_line(aes(yday(date),smooth,col=year),size=1)

```


# 4.
```{r}
set.seed(1993)
data("tissue_gene_expression")
tissues <- c("cerebellum", "hippocampus")
ind <- which(tissue_gene_expression$y %in% tissues)
y <- droplevels(tissue_gene_expression$y[ind])
x <- tissue_gene_expression$x[ind, ]
x <- x[, sample(ncol(x), 10)]
```

```{r}
#1.
fit<-train(x,y,method='lda')
fit

#2.
dat<-t(fit$final$means)
dat
dat %>% as_tibble() %>% 
  mutate(label=as.factor(rownames(dat))) %>%
  ggplot(aes(cerebellum,hippocampus,col=label,label=label))+
  geom_point()+geom_text()+theme(legend.position="none") 
#VOPP1 & PPME1 appear to be driving the algorithm


#3.
fit2<-train(x,y,method='qda')
fit2#lower accuracy than LDA

#4.

dat2<-t(fit2$final$means)
dat2
dat2 %>% as_tibble() %>%
  mutate(label=as.factor(rownames(dat))) %>%
  ggplot(aes(cerebellum,hippocampus,col=label,label=label))+
  geom_point()+geom_text()+theme(legend.position="none") 
#VOPP1 & PPME1 appear to be driving the algorithm
```


```